Finite Property Convex Elicitation Paper

### 2019-01-30 cvx-fin.tex
Fixed typo in prop 10

\begin{proposition}\label{prop:embed-link}
  If $\Gamma$ embeds a finite property $\gamma$, then it has a calibrated link $\psi$ to $\gamma$.
  Moreover, if a polyhedral loss $L$ elicits $\Gamma$, $\psi$ can be taken to be separated with respect to $L$.
\end{proposition}
\begin{proof}
  %\raf{I think you mean $\varphi^{-1}(u)$, but that is only defined on $\varphi(\R)$ (the embedded points).  Use Proposition~\ref{prop:embed-trim}, specifically trim.}
  Since the finite property $\gamma$ is embedded by $\Gamma$, we know that $\trim(\Gamma)$ is finite by Proposition~\ref{prop:embed-trim}, as is $\varphi(\R)$.
  Therefore, for every $u \in \reals^d$, consider two cases.
  First, if $u \in \varphi(\R)$, then $\psi(u) = \varphi^{-1}(u)$ suffices.
  Now, if $u \not\in\varphi(\R)$, then there is an equivalent report $w \in \varphi(\R)$ so that $\Gamma_u \subset \Gamma_w$.
  In such cases, construct $\psi(u) := \varphi^{-1}(w)$.
  If there is more than one equivalent report, choose one arbitrarily.
  Now, for any $p \in \simplex$ such that $u \in \Gamma(p)$, we also have that $w \in \Gamma(p)$, so $\psi(u) = \phi^{-1}(w) \in \gamma(p)$.

  For the second part of the statement, in order for $\psi$ to be separated, for $\epsilon > 0$, for each embedded point $u \in \reals^d$ and every $v \in B(\epsilon, u)$, we must observe $\psi(v) = \psi(u)$.
  If the loss $L$ is polyhedral, we want to show that we can construct a $\psi$ so that the above holds.

>>>>

\begin{proposition}\label{prop:embed-link}
  If $\Gamma$ embeds a finite property $\gamma$, then it has a calibrated link $\psi$ to $\gamma$.
  Moreover, if a polyhedral loss $L$ elicits $\Gamma$, $\psi$ can be taken to be separated with respect to $L$.
\end{proposition}
\begin{proof}
  %\raf{I think you mean $\varphi^{-1}(u)$, but that is only defined on $\varphi(\R)$ (the embedded points).  Use Proposition~\ref{prop:embed-trim}, specifically trim.}
  Since the finite property $\gamma$ is embedded by $\Gamma$, we know that $\trim(\Gamma)$ is finite by Proposition~\ref{prop:embed-trim}, as is $\varphi(\R)$.
  Therefore, for every $u \in \reals^d$, consider two cases.
  First, if $u \in \varphi(\R)$, then $\psi(u) = \varphi^{-1}(u)$ suffices.
  Now, if $u \not\in\varphi(\R)$, then there is a report $w \in \varphi(\R)$ so that $\Gamma_u \subset \Gamma_w$.
  In such cases, construct $\psi(u) := \varphi^{-1}(w)$.
  If there is more than one such report, choose one arbitrarily.
  Now, for any $p \in \simplex$ such that $u \in \Gamma(p)$, we also have that $w \in \Gamma(p)$, so $\psi(u) = \varphi^{-1}(w) \in \gamma(p)$.

  \jessiet{Hole jere: $j$-faces of the function.}
  For the second part of the statement, in order for $\psi$ to be separated, for $\epsilon > 0$, for each embedded point $u \in \reals^d$ and every $v \in B(\epsilon, u)$, we must observe $\psi(v) = \psi(u)$.
  If the loss $L$ is polyhedral, we want to show that we can construct a $\psi$ so that the above holds.
